A Motion Blur Resilient Fiducial Marker For Quadcopter Imaging

### 2014-05-29 WACV/paper.tex
Two column changes
1. Removed bullets in discussion 2. Added figures for setup

\begin{figure}
\centering
 \begin{subfigure}[b]{0.19\textwidth}
  \centering
  \includegraphics[width=0.8\linewidth]{intersense.jpg}
  Circular Data Matrix~\cite{NaimarkF02}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\textwidth}
 \centering
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit~\cite{ARToolkit02}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\textwidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\quad~\cite{Fiala05}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\textwidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.jpg}
  PiTag\quad~\cite{Pitag13}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\textwidth}
  \centering
  \includegraphics[width=\linewidth]{our_fiducial}
  Our Fiducial
 \end{subfigure}
 \caption{This figure shows the design of several existing fiducial markers.  While
 each code has their own pros and cons for various environments, none are
 designed to be recognized under motion blur.}
 \label{fig:previous_work}
\end{figure}

@@

\noindent\begin{minipage}[h!]{\textwidth}
\noindent\begin{minipage}{0.6\textwidth}
\includegraphics[width=\textwidth]{artag_pitag.pdf}
%\captionof{figure}{Blurred AR Tag and Pi--tag with various blur scales}
\end{minipage}
\begin{minipage}{0.35\textwidth}
%\captionof{table}{Recognition rate of AR Tag and Pi-tag fiducial marker atvarious blur scales}
\begin{tabularx}{\textwidth}{|Y|Y|Y|}
\cline{1-3}
\small{Blur} & \multicolumn{2}{c|}{ \small{Recognition Rate}}
\\\cline{2-3}
\small{Scale}& \small{PiTag} &	\small{ARTag} \\ \cline{1-3}
\small{15} & \small{100} & \small{100} \\ %\cline{1-3}
\small{30} & \small{0} & \small{100} \\  %\cline{1-3}
\small{35} & \small{0} & \small{19} \\ %\cline{1-3}
\small{50} & \small{0} & \small{0} \\ \cline{1-3}
\end{tabularx}
\end{minipage}
\captionof{figure}{Figure showing PiTag and ARTag blurred with various blur
scales at different orientations. Table on the right shows the recognition rate
(in percent) of both fiducial markers at various blur scales along all blur
orientations.  Recognition rates for both tags are significantly reduced due to
blur. For severe blur, detection is not possible.}
\label{fig:artag_pitag}
\end{minipage}

@@

We have implemented our algorithm in C++ using the OpenCV library.
Experiments were performed on a PC with Intel Core i7 processor(@3.4GHz) and 4GB RAM.
Source code to generate and recognize the code, as well as the data sets used in
this paper will be made publicly available.  Video clips
of collected data are provided in the supplementary material.

Our system has been tested on several image sequences captured from an AR Drone
quadcopter.  The drone was flown indoors looking at patterns attached to
various walls. Each image sequence contains frames of different fiducial
patterns. Sample output for each fiducial pattern is shown in Figure
\ref{fig:out_outputs}-(a) -- Figure \ref{fig:out_outputs}-(d). Our detection
process takes around 0.3 seconds which translates to slightly over three frames per second.

@@

@@

\noindent\begin{figure}
\begin{tabular}{c|c}
\begin{subfigure}[b]{0.65\linewidth}
\includegraphics[width=\linewidth]{recognition_rate.pdf}
\caption{Comparison of recognition rate of fiducials}
\label{fig:recognition_rate}
\end{subfigure}
&
\begin{subfigure}[b]{0.33\linewidth}
\begin{tabularx}{\textwidth}{|c|Y|}
\cline{1-2}
\footnotesize{Blur} & \footnotesize{Mean($\pm$std) error}  \\
\footnotesize{angle} & \footnotesize{(in pixels)}  \\
\cline{1-2}
\footnotesize{0} & \footnotesize{1.33 $\pm$ 0.40}  \\
\footnotesize{22} & \footnotesize{2.42 $\pm$ 1.05} \\
\footnotesize{45} & \footnotesize{1.46 $\pm$ 0.65}  \\
\footnotesize{67} & \footnotesize{2.39 $\pm$ 1.28}  \\
\footnotesize{90} & \footnotesize{1.83 $\pm$ 0.25}  \\ 
\cline{1-2}
\end{tabularx}
\caption{Center localization error}
\label{tab:blur_angle_center}
\end{subfigure}
\end{tabular}
\caption{(a): Comparison of recognition rate of the ARTag and our fiducials on
blur simulated data at various blur scales. It can be seen that except for the
fiducial with binary code ``00'', our fiducial patterns are recognized all times.
(b): Table showing the mean error and standard deviation of the localized fiducial center
versus the ground truth.  Error is computed for various blur angles over
different blur scales.}
\label{fig:simulated_blur}
\end{figure}

@@

\begin{figure}[hb!]
\begin{subfigure}{\textwidth}
\centering
  \includegraphics[width=0.4\linewidth]{output_00.jpg}
  \includegraphics[width=0.4\linewidth]{new_results/output_00.jpg}
  \caption{Binary code ``00''}
  \label{fig:output0}
\end{subfigure}
\begin{subfigure}{\textwidth}
\centering
  \includegraphics[width=0.4\linewidth]{output_01.jpg}
  \includegraphics[width=0.4\linewidth]{new_results/output_01.jpg}
  \caption{Binary code ``01''}
  \label{fig:output1}
\end{subfigure}
\begin{subfigure}{\textwidth}
\centering
  \includegraphics[width=0.4\linewidth]{output_10.jpg}
  \includegraphics[width=0.4\linewidth]{new_results/output_10.jpg}
  \caption{Binary code ``10''}
  \label{fig:output2}
\end{subfigure}
\begin{subfigure}{\textwidth}
\centering
  \includegraphics[width=0.4\linewidth]{output_11.jpg}
  \includegraphics[width=0.4\linewidth]{new_results/output_11.jpg}
  \caption{Binary code ``11''}
  \label{fig:output3}
  \end{subfigure}
  \caption{Sample outputs for two bit binary coded fiducials on different
  datasets. Class label attached to the detected fiducial is decimal equivalent
  of the binary code embedded in the detected fiducial.}
  \label{fig:out_outputs}
\end{figure}

\begin{table}[h!]
\caption{Comparison of recognition rate of ARTag and our fiducials on real
data captured through AR Drone. Each row shows analysis of a test
dataset captured for our fiducial with different binary code embedded in it.
Each dataset has around 1000 frames captured representing roughly two minutes of video each.}
\centering
\begin{tabularx}{\textwidth}{|c|Y|Y|Y|Y|}
\cline{1-5}
\multirow{2}{*}{Test \#} & \multirow{2}{*}{Number of Frames}
&\multirow{2}{*}{Binary Code} &\multicolumn{2}{c|}{Recognition Rate (\%)} \\
\cline{4-5} & & & ARTag & Our Fiducial \\\cline{1-5}
1 & 1205 & 00 &  65.6 & 86.5  \\ \cline{1-5}
2 & 1047 & 01 &  61.9 & 94.1  \\ \cline{1-5}
3 & 1102 & 10 &  62.4 & 92.74 \\ \cline{1-5}
4 & 1081 & 11 &  60.3 & 93.54  \\ \cline{1-5}
\end{tabularx}
\label{tab:recongition_accuracy}
\end{table}

\subsubsection{Comparison with BLUT}

@@

\begin{figure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_00/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_00/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_00/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_00/5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_00/6.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_00/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_00/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_00/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_00/output5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_00/output6.jpg}
\end{subfigure}
\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing ``00''
binary coded fiducial. Bottom: Output of our algorithm on the same image
sequence. BLUT is able to track the fiducial till the third frame, but from fourth
frame BLUT looses track of the fiducial. In first three frames, the size of the
fiducials is less but in fourth and fifth frame it is bigger, hinting at a sudden
forward movement of quadcopter.}
\label{fig:BLUT_compare_00}
\end{figure}

\begin{figure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_01/11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_01/12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_01/13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_01/14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_01/15.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_01/output11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_01/output12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_01/output13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_01/output14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_01/output15.jpg}
\end{subfigure}
\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing
``01'' binary coded fiducial. Bottom: Output of our algorithm on the same image
sequence. BLUT looses the track from the third frame.}
\label{fig:BLUT_compare_01}
\end{figure}

\begin{figure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/1.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/5.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output1.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output5.jpg}
\end{subfigure}
\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing
``10'' binary coded fiducial. Bottom: Output of our algorithm on the same image
sequence. From the second frame, BLUT looses track.}
\label{fig:BLUT_compare_10}
\end{figure}

\begin{figure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/6.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output6.jpg}
\end{subfigure}
\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing
``11'' binary coded fiducial. Bottom: Output of our algorithm on the same image
sequence. BLUT lost the track from third frame. There is sudden reversal of
direction from the quadcopter in the third frame. In first two frames, the quadcopter was
going up, but suddenly moved down.}
\label{fig:BLUT_compare_11}
\end{figure}

@@

We have demonstrated the effectiveness of our blur invariant fiducial both
synthetically and on real video clips captured from a quadcopter.   Our approach obtains
approximately 86-95\% recognition rate on fiducals in real scenes compared to existing codes
that are around 64\%.  We discuss some limitations of our approach in the following.

\noindent\textbf{Processing Time}~~Currently, our processing time (0.3 seconds
per frame) does not provide real-time performance.  As such, we currently
envision this will be used in an offline manner for performing analysis of
flight paths. Code profiling revealed that the Gabor filtering along the eight
directions takes most of the time (0.03 -- 0.04 seconds per orientation).  Either an
improved Gabor filter scheme is required or an alternative strategy for
detection is required.

\noindent\textbf{False Negatives}~~We found that sometimes our detection
algorithm fails to recognize our fiducial with binary code ``00'' when there is
large amount of blur.  The is because when there is too much blur, the innermost
ring's response in the Gabor output is too low and not detected properly.
This problem can be resolved by increasing the radius of innermost ring to
reduce the effect of blur on the innermost ring.

\noindent\textbf{Pose Estimation}~~We note that other markers are able to give
full pose estimation after detection.  However, we are only able to reliably detect
the center point and therefore cannot estimate pose.  Of course, if four
markers were used in a known order, pose could be estimated. The current
resolution of onboard camera will be main hurdle to clear before we can
effectively use multiple markers in each scene.

\noindent\textbf{Number of Fiducials}~~Currently, compared to ARTag fiducial
markers, we are able to generate less number of fiducials. Many applications in
robotics (e.g. quadcopter navigation) may not require large number of fiducial
markers as available by ARTag.  Most of the time, it is sufficient to have 4-6
different fiducial patterns. Still, we may be able to generate a larger number of
fiducials by using color backgrounds. This is an area interest for further
investigation.

>>>>

\begin{figure}
\centering
 \begin{subfigure}[b]{0.19\linewidth}
  \centering
  \includegraphics[width=0.8\linewidth]{intersense.jpg}
  Circular Data Matrix~\cite{NaimarkF02}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\linewidth}
 \centering
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit~\cite{ARToolkit02}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\linewidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\quad~\cite{Fiala05}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\linewidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.jpg}
  PiTag\quad~\cite{Pitag13}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\linewidth}
  \centering
  \includegraphics[width=\linewidth]{our_fiducial}
  Our Fiducial
 \end{subfigure}
 \caption{This figure shows the design of several existing fiducial markers.  While
 each code has their own pros and cons for various environments, none are
 designed to be recognized under motion blur.}
 \label{fig:previous_work}
\end{figure}

@@

\noindent\begin{figure}
\includegraphics[width=\linewidth]{artag_pitag.pdf}
%\captionof{figure}{Blurred AR Tag and Pi--tag with various blur scales}
%\captionof{table}{Recognition rate of AR Tag and Pi-tag fiducial marker atvarious blur scales}
\begin{tabularx}{\linewidth}{|Y|Y|Y|}
\cline{1-3}
\small{Blur} & \multicolumn{2}{c|}{ \small{Recognition Rate}}
\\\cline{2-3}
\small{Scale}& \small{PiTag} &	\small{ARTag} \\ \cline{1-3}
\small{15} & \small{100} & \small{100} \\ %\cline{1-3}
\small{30} & \small{0} & \small{100} \\  %\cline{1-3}
\small{35} & \small{0} & \small{19} \\ %\cline{1-3}
\small{50} & \small{0} & \small{0} \\ \cline{1-3}
\end{tabularx}
\captionof{figure}{Figure showing PiTag and ARTag blurred with various blur
scales at different orientations. Table on the right shows the recognition rate
(in percent) of both fiducial markers at various blur scales along all blur
orientations.  Recognition rates for both tags are significantly reduced due to
blur. For severe blur, detection is not possible.}
\label{fig:artag_pitag}
\end{figure}

@@

We have implemented our algorithm in C++ using the OpenCV library.
Experiments were performed on a PC with Intel Core i7 processor(@3.4GHz) and 4GB RAM.
Source code to generate and recognize the code, as well as the data sets used in
this paper will be made publicly available.  
%Video clips of collected data are provided in the supplementary material.

Our system has been tested on several image sequences captured from an AR Drone
quadcopter.  The drone was flown indoors looking at patterns attached to
various walls. Each image sequence contains frames of different fiducial
patterns. Sample output for each fiducial pattern is shown in Figure
\ref{fig:out_outputs}. Our detection process takes around 0.3 seconds which
translates to slightly over three frames per second.

@@

\begin{figure}[hb!]
\centering
  \includegraphics[width=0.4\linewidth]{output_00.jpg}
  \includegraphics[width=0.4\linewidth]{output_01.jpg}
  \includegraphics[width=0.4\linewidth]{output_10.jpg}
  \includegraphics[width=0.4\linewidth]{output_11.jpg}
  \caption{Sample outputs for two bit binary coded fiducials on different
  datasets. Class label attached to the detected fiducial is decimal equivalent
  of the binary code embedded in the detected fiducial.}
  \label{fig:out_outputs}
\end{figure}

@@

\noindent\begin{figure*}
\begin{tabular}{c|c}
\begin{subfigure}[b]{0.65\linewidth}
\includegraphics[width=\linewidth]{recognition_rate.pdf}
\caption{Comparison of recognition rate of fiducials}
\label{fig:recognition_rate}
\end{subfigure}
&
\begin{subfigure}[b]{0.33\linewidth}
\begin{tabularx}{\textwidth}{|c|Y|}
\cline{1-2}
\footnotesize{Blur} & \footnotesize{Mean($\pm$std) error}  \\
\footnotesize{angle} & \footnotesize{(in pixels)}  \\
\cline{1-2}
\footnotesize{0} & \footnotesize{1.33 $\pm$ 0.40}  \\
\footnotesize{22} & \footnotesize{2.42 $\pm$ 1.05} \\
\footnotesize{45} & \footnotesize{1.46 $\pm$ 0.65}  \\
\footnotesize{67} & \footnotesize{2.39 $\pm$ 1.28}  \\
\footnotesize{90} & \footnotesize{1.83 $\pm$ 0.25}  \\ 
\cline{1-2}
\end{tabularx}
\caption{Center localization error}
\label{tab:blur_angle_center}
\end{subfigure}
\end{tabular}
\caption{(a): Comparison of recognition rate of the ARTag and our fiducials on
blur simulated data at various blur scales. It can be seen that except for the
fiducial with binary code ``00'', our fiducial patterns are recognized all times.
(b): Table showing the mean error and standard deviation of the localized fiducial center
versus the ground truth.  Error is computed for various blur angles over
different blur scales.}
\label{fig:simulated_blur}
\end{figure*}

@@

\begin{table}[t!]
\caption{Comparison of recognition rate of ARTag and our fiducials on real
data captured through AR Drone. Each row shows analysis of a test
dataset captured for our fiducial with different binary code embedded in it.
Each dataset has around 1000 frames captured representing roughly two minutes of video each.}
\centering
\begin{tabularx}{\linewidth}{|c|Y|Y|Y|Y|}
\cline{1-5}
\multirow{2}{*}{Test \#} & {Number of frames}
&{Binary Code} &\multicolumn{2}{c|}{Recognition Rate (\%)} \\
\cline{4-5} & & & ARTag & Our Fiducial \\\cline{1-5}
1 & 1205 & 00 &  65.6 & 86.5  \\ \cline{1-5}
2 & 1047 & 01 &  61.9 & 94.1  \\ \cline{1-5}
3 & 1102 & 10 &  62.4 & 92.74 \\ \cline{1-5}
4 & 1081 & 11 &  60.3 & 93.54  \\ \cline{1-5}
\end{tabularx}
\label{tab:recongition_accuracy}
\end{table}

In another setup we arranged our fiducials on four sides of a box and revolved
quadcopter around it. Later, we repeated the process by replacing our fiducial
by AR Tags. Some intermediate frames are shown in Figure \ref{fig:setup}.

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_our/output_6/output_514.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_our/output_6/output_556.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_our/output_2/output_35.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_our/output_2/output_330.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_our/output_6/output_943.jpg}
\end{subfigure}
\caption{Figure showing intermediate frames captured by quadcopter while
revolving around our setup}
\label{fig:setup}
\end{figure*}
\subsubsection{Comparison with BLUT}

@@

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_00/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_00/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_00/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_00/5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_00/6.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_00/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_00/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_00/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_00/output5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_00/output6.jpg}
\end{subfigure}
\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing ``00''
binary coded fiducial. Bottom: Output of our algorithm on the same image
sequence. BLUT is able to track the fiducial till the third frame, but from fourth
frame BLUT looses track of the fiducial. In first three frames, the size of the
fiducials is less but in fourth and fifth frame it is bigger, hinting at a sudden
forward movement of quadcopter.}
\label{fig:BLUT_compare_00}
\end{figure*}

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_01/11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_01/12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_01/13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_01/14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_01/15.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_01/output11.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_01/output12.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_01/output13.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_01/output14.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_01/output15.jpg}
\end{subfigure}
\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing
``01'' binary coded fiducial. Bottom: Output of our algorithm on the same image
sequence. BLUT looses the track from the third frame.}
\label{fig:BLUT_compare_01}
\end{figure*}

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/1.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/5.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output1.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output5.jpg}
\end{subfigure}
\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing
``10'' binary coded fiducial. Bottom: Output of our algorithm on the same image
sequence. From the second frame, BLUT looses track.}
\label{fig:BLUT_compare_10}
\end{figure*}

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/6.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output6.jpg}
\end{subfigure}
\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing
``11'' binary coded fiducial. Bottom: Output of our algorithm on the same image
sequence. BLUT lost the track from third frame. There is sudden reversal of
direction from the quadcopter in the third frame. In first two frames, the quadcopter was
going up, but suddenly moved down.}
\label{fig:BLUT_compare_11}
\end{figure*}

@@

We have demonstrated the effectiveness of our blur invariant fiducial both
synthetically and on real video clips captured from a quadcopter.   Our approach obtains
approximately 86-95\% recognition rate on fiducals in real scenes compared to existing codes
that are around 64\%.  We discuss some limitations of our approach in the
section.
%\noindent\textbf{Processing Time}~~
Currently, our processing time (0.3 seconds per frame) does not provide
real-time performance.  As such, we currently envision this will be used in an
offline manner for performing analysis of flight paths. Code profiling revealed that the Gabor filtering along the eight
directions takes most of the time (0.03 -- 0.04 seconds per orientation).  Either an
improved Gabor filter scheme is required or an alternative strategy for
detection is required.
%\noindent\textbf{False Negatives}~~
We found that sometimes our detection
algorithm fails to recognize our fiducial with binary code ``00'' when there is
large amount of blur.  The is because when there is too much blur, the innermost
ring's response in the Gabor output is too low and not detected properly.
This problem can be resolved by increasing the radius of innermost ring to
reduce the effect of blur on the innermost ring. 
%\noindent\textbf{Pose Estimation}~~
We note that other markers are able to give
full pose estimation after detection.  However, we are only able to reliably detect
the center point and therefore cannot estimate pose.  Of course, if four
markers were used in a known order, pose could be estimated. The current
resolution of onboard camera will be main hurdle to clear before we can
effectively use multiple markers in each scene.
%\noindent\textbf{Number of Fiducials}~~
Currently, compared to ARTag fiducial markers, we are able to generate less
number of fiducials. Many applications in robotics (e.g. quadcopter navigation)
may not require large number of fiducial markers as available by ARTag.  Most
of the time, it is sufficient to have 4-6 different fiducial patterns. Still,
we may be able to generate a larger number of fiducials by using color
backgrounds. This is an area interest for further investigation.
